### 2016-01-14 doc/tutorial/windowsHowTo.Rmd
cleanup, add LLSVM writer

***SVMBridge Windows Tutorial***

1) Download R 3.2.x or later for Windows (32/64 bit) (https://cran.r-project.org/bin/windows/base/)

2) Download Rtools for R 3.2.x and later (https://cran.r-project.org/bin/windows/Rtools/)

3) Download Git for Windows (https://git-scm.com/downloads)

3) Install R and use the 32 bit option only

4) Install Rtools and use the 32 bit option only

5) Install Git

6) Start up the Git Bash and navigate into a directory in which you want to download SVMbridge to. For best compatibility,
   install SVMBridge into your home directory. Some tests may fail if you put it elsewhere.

7) Download the SVMBridge repository by using git clone in the git console 
   (git clone https://github.com/aydindemircioglu/SVMBridge.git)

8) Delete the makefile.win file, which is located in the src directory in SVMBridge.

@@

9) Start up R Gui and install following packages by typing "install.packages("package-name")" into the R Gui: BBmisc, stringr, 
    plyr, Rcpp, microbenchmark, R.utils, e1071, SparseM, testthat, knitr, devtools

>>>>

# SVMBridge Windows Quick Tutorial

- Download latest R for Windows (32/64 bit) (https://cran.r-project.org/bin/windows/base/)
- Download Rtools for R 3.2.x and later (https://cran.r-project.org/bin/windows/Rtools/)
- Install R and use the 32 bit option only
- Install Rtools and use the 32 bit option only
- Install SVMBridge by starting R and typing ```install.packages ("SVMBridge")```
- If SVMBridge was successfully installed, you can now execute the OS-specific tests. For this
you need testthat. To install testthat, ```install.packages ("testthat")```
- Then execute the tests by .....
- Now if the tests were succesful, you end up with a bunch of pre-compiled SVM software. Copy these over to a directory you like, e.g. C:\Programs\SVMSolver\. Alternatively, especially for those SVM solvers for which the **SVMBridge** has no support, download and compile the SVM software by yourself and also put it into a directory of your choice.

You're ready to test the SVMBridge.

- ...

@@
